### 2021-07-30 doc/thesis/chapters/results.tex
wip.....

>>>>

\begin{figure}%
  \centering
  \subfloat[\centering label 1]{{\includegraphics[trim=10 10 10 10,clip, width=0.45\textwidth]{img/matlab/lines_of_code_pie_chart_py} }}%
  \\
  %\hspace{\fill}
  \subfloat[\centering label 2]{{\includegraphics[trim=10 10 10 10,clip, width=0.45\textwidth]{img/matlab/lines_of_code_pie_chart_py} }}%
  %\hspace{\fill}
  \vspace{3cm}
  \subfloat[\centering label 3]{{\includegraphics[trim=10 10 10 10,clip, width=0.45\textwidth]{img/matlab/lines_of_code_pie_chart_py} }}

  \caption{Multiple Figures side by side}%
  \label{fig:example}%
\end{figure}
